Automatic Matching of Bullet Lands

### 2016-07-26 revision/response.Rmd

---
title: "Response to reviewers"
author: "Eric Hare, Heike Hofmann, Alicia Carriquiry"
date: "July 26, 2016"
output:
  pdf_document: default
  html_document: default
---

@@

    ***We selected random forests because the method has desirable attributes and can be easily ported to other forensic applications. We were not intending to provide new insights on random forests. The focus of the paper was to show the potential of combining a large number ofimage attributes to discriminate among bullets. As the forest ultimately predicted every land-to-land comparison properly, we felt that a comparison to other learning methods was outside the scope of this paper. Had a wider variety of data been available, there would likely be more variability in the predictions and a comparison to other learning methods would be prudent.***

# Reviewer B

4. The authors should discuss their work in the context of Nicholas Petraco’s work as well as other ongoing research endeavors in impression and pattern evidence. See https://www.ncjrs.gov/pdffiles1/nij/grants/239048.pdf The alignment method should have been compared with a standard method- See Patraco’s NIJ report for a couple of examples. As presented the novel component of the paper is the "twicing" for grooves combined with a loess fit to the remove curves from bullet images. I am not sure this is the authors intention. It would be interesting to compare this method with some of the classical methods from functional data analysis used for curve registration.

    ***Thank you for the comments. Using the cross correlation function as a method of alignment is actually pretty standard - the appropriate references are now included. We have attempted to better clarify the novel component of this work, by explaining openly and transparently describing each individual step of the analysis process, and providing the source code used to reproduce the findings.***

### 2016-07-26 revision/response.Rmd

---
title: "Response to reviewers"
author: "Eric Hare, Heike Hofmann, Alicia Carriquiry"
date: "July 26, 2016"
output:
  pdf_document: default
bibliography: references.bib
---

@@

    ***We selected random forests because the method has desirable attributes and can be easily ported to other forensic applications. We were not intending to provide new insights on random forests. The focus of the paper was to show the potential of combining a large number ofimage attributes to discriminate among bullets. As the forest ultimately predicted every land-to-land comparison properly, we felt that a comparison to other learning methods was outside the scope of this paper. Had a wider variety of data been available, there would likely be more variability in the predictions and a comparison to other learning methods would be prudent.***

# Reviewer B

4. The authors should discuss their work in the context of Nicholas Petraco’s work as well as other ongoing research endeavors in impression and pattern evidence. See https://www.ncjrs.gov/pdffiles1/nij/grants/239048.pdf The alignment method should have been compared with a standard method- See Patraco’s NIJ report for a couple of examples. As presented the novel component of the paper is the "twicing" for grooves combined with a loess fit to the remove curves from bullet images. I am not sure this is the authors intention. It would be interesting to compare this method with some of the classical methods from functional data analysis used for curve registration.

    ***Thank you for the comments. Using the cross correlation function as a method of alignment is actually pretty standard - the appropriate references are now included. We have attempted to better clarify the novel component of this work, by describing openly and transparently each individual step of the analysis process, and providing the source code used to reproduce the findings.***

@@

13. there is a lack of knowledge of the existing literature on statistical work performed on tool marks and firearms. For example, the work performed by Nicholas Petraco, Fabiano Riva, or Alan Zheng in the past 5 years is not mentioned. Instead, old research projects are mentioned, which mostly focus on manual identification. The authors need to discuss the novelty of their method (and how it potentially addresses the shortcomings of these recent methods)

    ***The point that the reviewer makes is valid.  While we were familiar with the computer-assisted approaches that have been proposed, practice still relies on human examination of potential candidates presented by a system such as NIBIN. We have added what we hope is an acceptably complete review of the literature in the revised manuscript.***

14. The authors would need to study (or at least discuss extensively) the ability of their method to capture the variability in bullet profiles over time (at interval of several dozen of bullets fired by the same weapon, when the weapon has been cleaned, or when the bullet was degraded by hitting a target). In addition, a dataset of 10 firearms (even consecutively manufactured) does not provide any information on the rarity of a particular bullet profile, and therefore does not address the second probability statement. Alternatively, the proposed metrics could be tested in a database searching situation, which has not been done.

    ***At the time of the submission of this manuscript, the 35 bullets from 10 barrels from Hamby set 252 were the only ones accessible to the public. They are part of Dr Zheng's efforts at NIST to provide a ballistics reference database. In the future more results will be available, but until then we are unable to provide a data-informed discussion of the very important issues raised by the reviewer. With that said, it has been shown that with repeated firings, minor degradation does occur, but that such minor degradation likely wouldn't prevent correct matching [@bachrach:2006]. It would be very interesting to study this further, but this unfortunately is outside the scope of this paper.***

@@

15. On a related subject, I believe that a random forest provides the probability that two bullets were fired by the same gun given the set of observations (Fig 19), not the probability of interest: the probability of two sets of observations given that the two bullets were fired by the same gun. The authors may want to revise some of the statements in their discussion and conclusion.

    ***The reviewer is correct in stating that two probabilities of interest are the probability of observing the data under the "same source" (same gun) hypothesis or under the "different source" hypothesis.  An empirical approach to get at those two probabilities is to derive the distribution of scores when two bullets are known to have been fired by the same gun and the distribution of scores when two bullets are known to have been fired by different guns.  We have actually derived those two distributions and included them in the revised manuscript.***

@@

16. I am concerned by the assumption of independence of between the different lands on a given bullet that the authors seems to use in their error rates calculations (and ROC curves). The assumption seems unreasonable since as soon as a land has been paired between two bullets, it seems that it becomes more likely to pair the other lands. In other words, I believe that the authors need to redo their error rate measurements, but using bullets as their experimental units and not lands. I am also concerned by the overwhelming majority of non-matches, this must certainly artificially increase the rate of correct exclusion and distort the data.

    ***Assuming independence between the lands of each barrel is certainly not realistic in practice, however, by assuming independence we make the task of matching harder for the algorithm. This also has the benefit of potentially being more useful for degraded data, where we may not have a full set of six groove-to-groove scans. Based on the actual numerical values of features derived from each of the lands, an independence assumption is not unrealistic, because the features do not exhibit any clustering associated to barrel. The technique suggested by the reviewer could be solved using a hierarchical approach to matching, and we agree with the assessment that it would likely decrease the error rates.***

### 2016-07-26 imaging-paper.Rnw
Paper updates

\begin{figure}[hbtp]
\centering
\includegraphics[width=.65\columnwidth]{images/matchup-rgl-copy.png}
\caption{\label{fig:manualmatch-rgl}3D view of the manually adjusted side-by-side comparison of bullet~1-5 and bullet 2-1 after removing the curvature. \hh{Bullet 2-1 is shaded light grey in the background.}}
\end{figure}

@@

\subsection{Horizontal alignment}
Signatures of each of the two lands, 1-5 and 2-1,  in Figure~\ref{fig:manualmatch-rgl} are shown in Figure~\ref{fig:cross100} extracted at a height of $x = 100\mu m$. Striation marks show up in these representations as peaks and valleys.  The individual characteristics are quite prominent and, again, suggest a match between the lands. A horizontal shift of one of the signatures (result shown in Fig~\ref{fig:crosscutX}) emphasizes the strong similarities. 
%
\begin{figure}[hbtp]
\centering
\begin{subfigure}[b]{.49\textwidth}\centering
\caption{Raw bullet land signatures.\label{fig:crosscut}}{%
<<crosscuts, echo=FALSE, dependson='twolands100', fig.width=7, fig.height=3, out.width='\\textwidth'>>=
lof$bulletname <- scrubPath(lof$bullet)
qplot(y, resid, group=bulletname, colour=bulletname, data=lof, 
      geom="line") + 
  scale_colour_manual("", values=cols) + theme_bw() +
  theme(legend.position = c(1, 1.1), legend.justification=c("right", "top"),
        legend.background = element_rect(fill=alpha('white', 0.4))) + 
  ylab("Residuals of loess fit")
@
    }
\end{subfigure}    
\begin{subfigure}[b]{.49\textwidth}\centering
    \caption{Aligned signatures.\label{fig:crosscutX}}{%
<<crosscutsX, echo=FALSE, dependson='twolands100', fig.width=7, fig.height=3, out.width='\\textwidth'>>=
lofY$bulletname <- scrubPath(lofY$bullet)
qplot(y+min(lof$y), resid, group=bulletname, colour=bulletname, data=lofY, 
      geom="line") + xlab("y") +
  scale_colour_manual("", values=cols) + theme_bw() +
  theme(legend.position = c(1, 1.1), legend.justification=c("right", "top"),
        legend.background = element_rect(fill=alpha('white', 0.4))) + 
  ylab("Residuals of loess fit")
@
    }
\end{subfigure}
\caption{\label{fig:cross100}Signatures of bullets 1-5 and 2-1 taken at  heights of $x = 100\mu m$. A horizontal shift of the values of bullet~1-5 to the right shows the similarity of the striation marks.}
\end{figure}
%
\hh{For this alignment we use the cross-correlation function to find a maximal amount of agreement between the signatures~\cite{bachrach:2002, chu:2010, vorburger:2011, thompson:2013}.}
This horizontal shift is based on the cross-correlation between the two signatures: let $f(t)$ and $g(t)$ define the signature values  at $t$, where $t$ are locations between 0~$\mu m$ and about 2500~$\mu m$, 1.5625~$\mu m$ apart.
The cross-correlation between $f$ and $g$ at lag $k$ is then defined as
\[
(f * g) (k) = \sum_t f(t+k) g(t),
\]
with suitably defined limits for the summation. % (because variances of $f$ and $g$ do not change, the above equation is proportional to the correlation).

@@

ggplot(data=subset(rocs, auc > 0.5)) +
  geom_ribbon(aes(x=`FALSE`, ymax=`TRUE`, ymin=0), alpha=0.2) +
  geom_line(aes(x=`FALSE`,y=`TRUE`))+ theme_bw() + 
  xlab("False negative rate") + 
  ylab("False positive rate") + facet_wrap(facets=~varLabel, ncol=4) + 
  geom_label(x=1, y=0, aes(label=labels), data=labels, hjust=1, vjust=0) + 
  geom_abline(linetype=2) + 
  geom_point(aes(x=`FALSE`, y=`TRUE`), data=eer, size=2.5) +
  geom_label(x=1, y=0.125, aes(label=labels), data=eer, hjust=1, vjust=0)
@
\caption{\label{fig:rocs}ROC curves for all of the features described in section~\ref{sec:algorithm}. Variables are sorted according to their area under the curve (AUC). \hh{The equal error rate (EER) is marked by a point on the ROC curve.} Except for the distance $D$ between signatures, all individual features derived from the surface measurements and the aligned striation marks are more predictive than the maximal CMS. }
\end{figure}

@@

%Similarly, the Euclidean distance $D$ between two signatures is strongly correlated to known matches. Out of the 48 pairs of land-to-land signatures with a distance of less than .25, 47 correspond to known matches (the single known mismatch consists of a pair of signatures that both are very flat with peaks and valleys of less than 1.5$\mu m$). %The average distance between known matches in the Hamby study is $\Sexpr{mean(bstats$D[bstats$match])}\mu m$ with a standard deviation of $\Sexpr{sd(bstats$D[bstats$match])}\mu m$; while known mismatches have an average  distance of  $\Sexpr{mean(bstats$D[!bstats$match])}\mu m$ with a standard deviation of $\Sexpr{sd(bstats$D[!bstats$match])}\mu m$.
All of the features in Figure~\ref{fig:densities} show large, if not significant, differences between matches and non-matches. The predictive power of each one of these features is shown in the form of the Receiving Operating Characteristic (ROC) curves in Figure~\ref{fig:rocs}. The features are arranged in descending order according to the area under the curve (AUC).
\hh{XXX The dots mark the equal error rate, i.e. the location on the ROC curve, where false positive and false negative error rates are the same. The smaller the value, the better. We see that in this instance a low EER goes hand in hand with high predictive power as measured in AUC. XXX HH: do we need to say more about EERs?}
The feature with the highest individual predictive power is $S$, the sum of the average heights of two signatures at peaks and valleys. The maximal number of CMS is only in the seventh position here. The overall high AUC values indicate that we can successfully employ machine learning methods to distinguish matches from non-matches.
%Table~\ref{tab:importance} shows an overview in the averages and corresponding standard deviations of the set of feature variables derived in section~\ref{sec:algorithm} from the 3D topological surface measurements. There are quite large differences in these averages, indicating

@@

We have presented an algorithm which detects the most prominent but least relevant structure of a bullet from a firearms identification perspective, removes these features, and produces residuals which allow for the easy identification of markings. We have generalized this algorithm to align the residuals from two bullets to automatically determine whether they are matches. We created a random forest model using many of the features to provide a probabilistic assessment of the quality of a match, along with the most relevant features. \eh{Matching bullets is clearly not a single step, but rather a composition of a number of data analysis tasks which each deserve attention. With no scientific standards in place, our intent is to explain one approach to addressing these tasks, while documenting all steps and providing all code so other researchers and forensic scientists can reproduce and expand on our findings.}

@@

By suggesting an automated algorithm that first removes class characteristics, such as the grooves and the curvature of the bullet to reveal the region of the  land, then identifies peaks and valleys on this land, we reduce subjectivity and with it possible sources of bias. In particular, `the concept of counting striations is subjective and based on experience'~\citep{miller:1998}. \eh{The steps outlined in this paper could also help explore other important forensic science problems. In particular, more general toolmark examination can benefit from this detection and removal of the overall structure and the extraction of features from deviations of this structure.}

>>>>

\begin{figure}[hbtp]
\centering
\includegraphics[width=.65\columnwidth]{images/matchup-rgl-copy.png}
\caption{\label{fig:manualmatch-rgl}3D view of the manually adjusted side-by-side comparison of bullet~1-5 and bullet 2-1 after removing the curvature. Bullet 2-1 is shaded light grey in the background.}
\end{figure}

@@

\subsection{Horizontal alignment}
Signatures of each of the two lands, 1-5 and 2-1,  in Figure~\ref{fig:manualmatch-rgl} are shown in Figure~\ref{fig:cross100} extracted at a height of $x = 100\mu m$. Striation marks show up in these representations as peaks and valleys.  The individual characteristics are quite prominent and, again, suggest a match between the lands. A horizontal shift of one of the signatures (result shown in Fig~\ref{fig:crosscutX}) emphasizes the strong similarities. 
%
\begin{figure}[hbtp]
\centering
\begin{subfigure}[b]{.49\textwidth}\centering
\caption{Raw bullet land signatures.\label{fig:crosscut}}{%
<<crosscuts, echo=FALSE, dependson='twolands100', fig.width=7, fig.height=3, out.width='\\textwidth'>>=
lof$bulletname <- scrubPath(lof$bullet)
qplot(y, resid, group=bulletname, colour=bulletname, data=lof, 
      geom="line") + 
  scale_colour_manual("", values=cols) + theme_bw() +
  theme(legend.position = c(1, 1.1), legend.justification=c("right", "top"),
        legend.background = element_rect(fill=alpha('white', 0.4))) + 
  ylab("Residuals of loess fit")
@
    }
\end{subfigure}    
\begin{subfigure}[b]{.49\textwidth}\centering
    \caption{Aligned signatures.\label{fig:crosscutX}}{%
<<crosscutsX, echo=FALSE, dependson='twolands100', fig.width=7, fig.height=3, out.width='\\textwidth'>>=
lofY$bulletname <- scrubPath(lofY$bullet)
qplot(y+min(lof$y), resid, group=bulletname, colour=bulletname, data=lofY, 
      geom="line") + xlab("y") +
  scale_colour_manual("", values=cols) + theme_bw() +
  theme(legend.position = c(1, 1.1), legend.justification=c("right", "top"),
        legend.background = element_rect(fill=alpha('white', 0.4))) + 
  ylab("Residuals of loess fit")
@
    }
\end{subfigure}
\caption{\label{fig:cross100}Signatures of bullets 1-5 and 2-1 taken at  heights of $x = 100\mu m$. A horizontal shift of the values of bullet~1-5 to the right shows the similarity of the striation marks.}
\end{figure}
%
For this alignment we use the cross-correlation function to find a maximal amount of agreement between the signatures~\cite{bachrach:2002, chu:2010, vorburger:2011, thompson:2013}.
This horizontal shift is based on the cross-correlation between the two signatures: let $f(t)$ and $g(t)$ define the signature values  at $t$, where $t$ are locations between 0~$\mu m$ and about 2500~$\mu m$, 1.5625~$\mu m$ apart.
The cross-correlation between $f$ and $g$ at lag $k$ is then defined as
\[
(f * g) (k) = \sum_t f(t+k) g(t),
\]
with suitably defined limits for the summation. % (because variances of $f$ and $g$ do not change, the above equation is proportional to the correlation).

@@

ggplot(data=subset(rocs, auc > 0.5)) +
  geom_ribbon(aes(x=`FALSE`, ymax=`TRUE`, ymin=0), alpha=0.2) +
  geom_line(aes(x=`FALSE`,y=`TRUE`))+ theme_bw() + 
  xlab("False negative rate") + 
  ylab("False positive rate") + facet_wrap(facets=~varLabel, ncol=4) + 
  geom_label(x=1, y=0, aes(label=labels), data=labels, hjust=1, vjust=0) + 
  geom_abline(linetype=2) + 
  geom_point(aes(x=`FALSE`, y=`TRUE`), data=eer, size=2.5) +
  geom_label(x=1, y=0.125, aes(label=labels), data=eer, hjust=1, vjust=0)
@
\caption{\label{fig:rocs}ROC curves for all of the features described in section~\ref{sec:algorithm}. Variables are sorted according to their area under the curve (AUC). The equal error rate (EER) is marked by a point on the ROC curve. Except for the distance $D$ between signatures, all individual features derived from the surface measurements and the aligned striation marks are more predictive than the maximal CMS. }
\end{figure}

@@

%Similarly, the Euclidean distance $D$ between two signatures is strongly correlated to known matches. Out of the 48 pairs of land-to-land signatures with a distance of less than .25, 47 correspond to known matches (the single known mismatch consists of a pair of signatures that both are very flat with peaks and valleys of less than 1.5$\mu m$). %The average distance between known matches in the Hamby study is $\Sexpr{mean(bstats$D[bstats$match])}\mu m$ with a standard deviation of $\Sexpr{sd(bstats$D[bstats$match])}\mu m$; while known mismatches have an average  distance of  $\Sexpr{mean(bstats$D[!bstats$match])}\mu m$ with a standard deviation of $\Sexpr{sd(bstats$D[!bstats$match])}\mu m$.
All of the features in Figure~\ref{fig:densities} show large, if not significant, differences between matches and non-matches. The predictive power of each one of these features is shown in the form of the Receiving Operating Characteristic (ROC) curves in Figure~\ref{fig:rocs}. The features are arranged in descending order according to the area under the curve (AUC).
The dots mark the equal error rate, i.e. the location on the ROC curve, where false positive and false negative error rates are the same. The smaller the value, the better. We see that in this instance a low EER goes hand in hand with high predictive power as measured in AUC.
The feature with the highest individual predictive power is $S$, the sum of the average heights of two signatures at peaks and valleys. The maximal number of CMS is only in the seventh position here. The overall high AUC values indicate that we can successfully employ machine learning methods to distinguish matches from non-matches.
%Table~\ref{tab:importance} shows an overview in the averages and corresponding standard deviations of the set of feature variables derived in section~\ref{sec:algorithm} from the 3D topological surface measurements. There are quite large differences in these averages, indicating

@@

We have presented an algorithm which detects the most prominent but least relevant structure of a bullet from a firearms identification perspective, removes these features, and produces residuals which allow for the easy identification of markings. We have generalized this algorithm to align the residuals from two bullets to automatically determine whether they are matches. We created a random forest model using many of the features to provide a probabilistic assessment of the quality of a match, along with the most relevant features. Matching bullets is clearly not a single step, but rather a sequence of a number of data analysis tasks which each deserve attention. As there is no scientific standard in place at this point in time, our intent is to explain one approach to addressing these tasks, while documenting all steps and providing all code so other researchers and forensic scientists can reproduce and expand on our findings.

@@

By suggesting an automated algorithm that first removes class characteristics, such as the grooves and the curvature of the bullet to reveal the region of the  land, then identifies peaks and valleys on this land, we reduce subjectivity and with it possible sources of bias. In particular, `the concept of counting striations is subjective and based on experience'~\citep{miller:1998}. The steps outlined in this paper could also help explore other important forensic science problems. In particular, more general toolmark examination can benefit from this detection and removal of the overall structure and the extraction of features from deviations of this structure.

### 2016-07-26 imaging-paper.tex
Paper updates

\end{knitrout}
    }
\end{subfigure}
\caption{\label{fig:cross100}Signatures of bullets 1-5 and 2-1 taken at  heights of $x = 100\mu m$. A horizontal shift of the values of bullet~1-5 to the right shows the similarity of the striation marks.}
\end{figure}
%
\hh{For this alignment we use the cross-correlation function to find a maximal amount of agreement between the signatures~\cite{bachrach:2002, chu:2010, vorburger:2011, thompson:2013}.}
This horizontal shift is based on the cross-correlation between the two signatures: let $f(t)$ and $g(t)$ define the signature values  at $t$, where $t$ are locations between 0~$\mu m$ and about 2500~$\mu m$, 1.5625~$\mu m$ apart.
The cross-correlation between $f$ and $g$ at lag $k$ is then defined as
\[
(f * g) (k) = \sum_t f(t+k) g(t),
\]
with suitably defined limits for the summation. % (because variances of $f$ and $g$ do not change, the above equation is proportional to the correlation).

@@

\end{knitrout}
\caption{\label{fig:rocs}ROC curves for all of the features described in section~\ref{sec:algorithm}. Variables are sorted according to their area under the curve (AUC). \hh{The equal error rate (EER) is marked by a point on the ROC curve.} Except for the distance $D$ between signatures, all individual features derived from the surface measurements and the aligned striation marks are more predictive than the maximal CMS. }
\end{figure}

@@

%Similarly, the Euclidean distance $D$ between two signatures is strongly correlated to known matches. Out of the 48 pairs of land-to-land signatures with a distance of less than .25, 47 correspond to known matches (the single known mismatch consists of a pair of signatures that both are very flat with peaks and valleys of less than 1.5$\mu m$). %The average distance between known matches in the Hamby study is $mean(bstats$D[bstats$match])\mu m$ with a standard deviation of $sd(bstats$D[bstats$match])\mu m$; while known mismatches have an average  distance of  $mean(bstats$D[!bstats$match])\mu m$ with a standard deviation of $sd(bstats$D[!bstats$match])\mu m$.
All of the features in Figure~\ref{fig:densities} show large, if not significant, differences between matches and non-matches. The predictive power of each one of these features is shown in the form of the Receiving Operating Characteristic (ROC) curves in Figure~\ref{fig:rocs}. The features are arranged in descending order according to the area under the curve (AUC).
\hh{XXX The dots mark the equal error rate, i.e. the location on the ROC curve, where false positive and false negative error rates are the same. The smaller the value, the better. We see that in this instance a low EER goes hand in hand with high predictive power as measured in AUC. XXX HH: do we need to say more about EERs?}
The feature with the highest individual predictive power is $S$, the sum of the average heights of two signatures at peaks and valleys. The maximal number of CMS is only in the seventh position here. The overall high AUC values indicate that we can successfully employ machine learning methods to distinguish matches from non-matches.
%Table~\ref{tab:importance} shows an overview in the averages and corresponding standard deviations of the set of feature variables derived in section~\ref{sec:algorithm} from the 3D topological surface measurements. There are quite large differences in these averages, indicating

>>>>

\end{knitrout}
    }
\end{subfigure}
\caption{\label{fig:cross100}Signatures of bullets 1-5 and 2-1 taken at  heights of $x = 100\mu m$. A horizontal shift of the values of bullet~1-5 to the right shows the similarity of the striation marks.}
\end{figure}
%
For this alignment we use the cross-correlation function to find a maximal amount of agreement between the signatures~\cite{bachrach:2002, chu:2010, vorburger:2011, thompson:2013}.
This horizontal shift is based on the cross-correlation between the two signatures: let $f(t)$ and $g(t)$ define the signature values  at $t$, where $t$ are locations between 0~$\mu m$ and about 2500~$\mu m$, 1.5625~$\mu m$ apart.
The cross-correlation between $f$ and $g$ at lag $k$ is then defined as
\[
(f * g) (k) = \sum_t f(t+k) g(t),
\]
with suitably defined limits for the summation. % (because variances of $f$ and $g$ do not change, the above equation is proportional to the correlation).

@@

\end{knitrout}
\caption{\label{fig:rocs}ROC curves for all of the features described in section~\ref{sec:algorithm}. Variables are sorted according to their area under the curve (AUC). The equal error rate (EER) is marked by a point on the ROC curve. Except for the distance $D$ between signatures, all individual features derived from the surface measurements and the aligned striation marks are more predictive than the maximal CMS. }
\end{figure}

@@

%Similarly, the Euclidean distance $D$ between two signatures is strongly correlated to known matches. Out of the 48 pairs of land-to-land signatures with a distance of less than .25, 47 correspond to known matches (the single known mismatch consists of a pair of signatures that both are very flat with peaks and valleys of less than 1.5$\mu m$). %The average distance between known matches in the Hamby study is $mean(bstats$D[bstats$match])\mu m$ with a standard deviation of $sd(bstats$D[bstats$match])\mu m$; while known mismatches have an average  distance of  $mean(bstats$D[!bstats$match])\mu m$ with a standard deviation of $sd(bstats$D[!bstats$match])\mu m$.
All of the features in Figure~\ref{fig:densities} show large, if not significant, differences between matches and non-matches. The predictive power of each one of these features is shown in the form of the Receiving Operating Characteristic (ROC) curves in Figure~\ref{fig:rocs}. The features are arranged in descending order according to the area under the curve (AUC).
The dots mark the equal error rate, i.e. the location on the ROC curve, where false positive and false negative error rates are the same. The smaller the value, the better. We see that in this instance a low EER goes hand in hand with high predictive power as measured in AUC.
The feature with the highest individual predictive power is $S$, the sum of the average heights of two signatures at peaks and valleys. The maximal number of CMS is only in the seventh position here. The overall high AUC values indicate that we can successfully employ machine learning methods to distinguish matches from non-matches.
%Table~\ref{tab:importance} shows an overview in the averages and corresponding standard deviations of the set of feature variables derived in section~\ref{sec:algorithm} from the 3D topological surface measurements. There are quite large differences in these averages, indicating
